Project Light

### 2015-09-02 paper/paper.tex
some fixes and minor improvements in the introduction

The Internet of Things (IoT) is becoming more and more reality every day.
It consists of small devices (called \textit{motes}), which are connected to the public Internet.
They work together to allow us monitoring and controlling several kinds of real-world systems, % SOURCE!
e.g. motes collecting information about parking lot occupancy allowing drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.

In the last decades, the rise embedded systems changed our daily lives. % Source?
However, these systems often had limited networking capabilities or at least used their own, proprietary and thus unaccessible network technology.
Because of the huge variety if valuable possibilities, the impact of embedded systems will be advanced even further within the IoT.

However, this comes at a price: by being accessible from the Internet, the attack surface of such systems is much larger than traditional embedded system had to face.
New, adapted security measurements had to be developed and implemented to react to this.
For example, Adaptive Key Establishment Scheme (AKES) provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices. % SOURCE!
Nevertheless, one problem remains: IoT setups usually consist of plentiful nodes which all need to be initialized with keying material and parameters.
This is a major problem, because typical motes lack of input/output devices which are securely usable without configured networking.

One possibility is to plug a wire to each and every node in order to initialize it.
However, there are two downsides: first, a typical IoT setup consist of too many devices to be plugging a feasible solution. Second, attackers may have physical access to motes, so jacks on the mote (e.g. JTAG) are a dangerous security threat.

Another approach is to pre-initialize the keys in the factory.
This would mean that either there is a small set of assigned keys, which would lead to vulnerabilities to brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes. However, they need to be as cheap as possible in order to be be affordable in great numbers.}.
Anyway, pre-initialization requires somebody other than the user/installer to know the keys, which diminishes security.

@@

There are several advantages of this method.
Light sensors are smaller and less misusable than jacks.
The physics of light is well understood by non-technical people, in contrast to radio waves.
Thus, leaking of the wireless sent information is less likely.
Moreover, multiple devices could be programmed concurrently by just placing them next to each other.

We implemented prototype for an Android smart phone and a Contiki\footnote{http://www.contiki-os.org/} mote.
Contiki is an open source, state-of-the-art operating system for IoT devices.
For the Android phone, we implemented two versions of a light emitting application.
We have tested some techniques to make the transmission error-prone.
Besides, we examined how fast the whole transmission could become while maintaining a high chance of correctness.

>>>>

The Internet of Things (IoT) is becoming more and more reality every day.
It consists of small devices (called \textit{motes}), which are connected to the public Internet.
They work together, allowing monitoring and controlling of several kinds of real-world systems. % SOURCE!
E.g., motes collecting information about parking lot occupancy allowing car drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.

In the last decades, the rise embedded systems changed daily lives. % Source?
However, these systems often had limited networking capabilities or at least used their own, proprietary and thus unaccessible network technology.
Because of the huge variety of valuable possibilities, the impact of embedded systems will be advanced even further within the IoT.

However, this comes at a price: by being accessible from the Internet, the attack surface of such systems is much larger than that of traditional embedded systems.
New, adapted security measurements had to be developed and implemented to react to this.
For example, Adaptive Key Establishment Scheme (AKES) provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices. % SOURCE!
Nevertheless, one problem remains: IoT setups usually consist of plentiful nodes which all need to be initialized with keying material and parameters.
This is a major problem, because typical motes lack of input/output devices which are securely usable without configured networking.

One possibility is to plug a wire to each and every node in order to initialize it.
However, there are two downsides: first, a typical IoT setup consist of too many devices to be plugging a feasible solution. Second, in most installations, attackers may have physical access to motes, so jacks on the mote (e.g. JTAG) are a dangerous security threat.

Another approach is to pre-initialize the keys in the factory.
This would mean that either there is a small set of assigned keys, which would lead to vulnerabilities to brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes, but they need to be as cheap as possible in order to be be affordable in great numbers.}.
Anyway, pre-initialization requires somebody other than the user/installer to know the keys, which diminishes security.

@@

There are several advantages of this method.
Light sensors are smaller and less misusable than jacks.
The physics of light is well understood by non-technical people, in contrast to radio waves.
Thus, leaking of the wireless sent secrets is less likely.
Moreover, multiple devices could be programmed concurrently by just placing them next to each other.

We implemented prototype for an Android smart phone and a Contiki\footnote{http://www.contiki-os.org/} mote.
Contiki is an open source, state-of-the-art operating system for IoT devices.
For Android phones, we implemented two versions of a light emitting application.
We also tested some techniques to make the transmission error-prone.
Besides, we examined how fast the whole transmission could become while maintaining a high chance of correctness.
